Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-02-18 paper/manuscript.Rmd
Fix corresponding author in manuscript

**Author for correspondence:** Daniel B. Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand

>>>>

**Author for correspondence:** E. Fernando Cagua (efc29@uclive.av.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
